---
title: "Untitled"
format: html
editor: visual
---

## Import data

1.  Raw data from Pavlovia (N = 139 BU students)
2.  Demographics data from Qualtrics (BU students)

```{r}
library(tidyverse)
```

### Raw data from Pavlovia (N = 139 BU students)

```{r}

data_dir <- "RAW_DATA_BU"

csv_files <- list.files(path = data_dir, pattern = "\\.csv$", full.names = TRUE)

# Read and combine CSV files, column types to character
combined_data <- csv_files %>%
  map_dfr(~ read_csv(.x, col_types = cols(.default = "c")), .id = "source") %>%
  mutate(dob = as.Date(`DOB (DD/MM/YEAR)`, format = "%d/%m/%Y"),
         vptCorrect = as.logical(vptCorrect))

library(lubridate)

nationality = c("British", "british", "British", "BRITISH", "British/ Portuguese", "England", 
                       "english", "English", "UK", "United Kingdom", "white", "White", 
                       "White - British", "white british", "White British", 
                "Brisith", "Briitish")

language = c("english", "English", "ENGLISH")

participant_info <- combined_data %>%
  dplyr::select(participant, group, `DOB (DD/MM/YEAR)`, Age, Nationality,
                `Language you learned multiplication table`, date, frameRate) %>%
  distinct() %>%
  mutate(Nationality = case_when(
    Nationality %in% nationality ~ "UK", TRUE ~ Nationality)) %>%
  dplyr::filter(Nationality == "UK") %>%
  rename(dob = `DOB (DD/MM/YEAR)`) %>%
  rename(lang_mult = `Language you learned multiplication table`) %>%
    mutate(lang_mult = case_when(
    lang_mult %in% language ~ "English", TRUE ~ lang_mult)) %>%
  rename(age = Age) %>%
    mutate(date = ymd_hms(date), 
           dob = dmy(dob), 
           age = as.numeric(interval(dob, date) / dyears(1)))%>% 
  write_csv("derivative/participant_info_UK.csv")
  
```

## Qualtrics Data (UK)

```{r}

selected_cols <- c("ethnicity_1", "ethnicity_2", "ethnicity_3", "ethnicity_4",
                   "ethnicity_5", "ethnicity_6")

cols_to_pivot <- c("multilingual_1", "multilingual_1_TEXT", 
                   "multilingual_2", "multilingual_2_TEXT",
                   "multilingual_3", "multilingual_3_TEXT", 
                   "multilingual_4", "multilingual_4_TEXT",
                   "multilingual_5", "multilingual_5_TEXT", 
                   "multilingual_6", "multilingual_6_TEXT",
                   "multilingual_7", "multilingual_7_TEXT", 
                   "multilingual_8", "multilingual_8_TEXT",
                   "multilingual_9", "multilingual_9_TEXT", 
                   "multilingual_10", "multilingual_10_TEXT")

qualtrics_uk <- read_csv("RAW_Demo/qualtrics_demo_UK.csv") |> 
  slice(3: n())|>
  dplyr::select(id, nationality, gender, maritalstatus, eduLevel, 
                ParentsEdu,	income,
                ethnicity_1, ethnicity_2, ethnicity_3, 
                ethnicity_4, ethnicity_5, ethnicity_6, 
                employment, major, handedness, Medicalhistory, developmentHist, 
                nativelanguage, lingualAbility, 
                multilingual_1, multilingual_1_TEXT, multilingual_2, multilingual_2_TEXT,
multilingual_3, multilingual_3_TEXT, multilingual_4, multilingual_4_TEXT,
multilingual_5, multilingual_5_TEXT, multilingual_6, multilingual_6_TEXT,
multilingual_7, multilingual_7_TEXT, multilingual_8, multilingual_8_TEXT,
multilingual_9, multilingual_9_TEXT, multilingual_10, multilingual_10_TEXT,
                mathlanguage_1, multiplylanguage, schooltype_1, 
                difficultiesmath, learnmultiplytable, peercomparison, 
                peercomparison2, rateownfluency_1,
                dyslexia,	mathanxious,	examanxious,	memory) |>
  rename(participant = id) |>
  pivot_longer(cols = all_of(selected_cols), 
               names_to = "ethnicity_column", 
               values_to = "ethnicity_value")|>
  dplyr::filter(!is.na(ethnicity_value)) |>
  dplyr::filter(nationality != "Others") |>
  select(-ethnicity_column) |>
  distinct(participant, .keep_all = TRUE) |>
  mutate(mathlanguage_1 = case_when(
    mathlanguage_1 %in% c("english", "English", "ENGLISH", 
                          "5", "6", "english/ arabic", "Buryfields") ~ "English", 
    TRUE ~ mathlanguage_1  
  ))|>
  mutate(multiplylanguage = case_when(
    multiplylanguage %in% c("english", "English", "ENGLISH", "Englsih", "Engliah",
                            "english / sometimes arabic") ~ "English",
    TRUE ~ multiplylanguage  
  )) |>
  mutate(schooltype_1 = case_when(
    schooltype_1 %in% c("Catholic state school", "Christian School",
                        "Church of England/academy", "faith school", "Faith school",
                        "Faith School", "faith schools") ~ "Faith",
    TRUE ~ schooltype_1  
  )) |>
  mutate(schooltype_1 = case_when(
    grepl("public", schooltype_1, ignore.case = TRUE) ~ "Public",
    grepl("private", schooltype_1, ignore.case = TRUE) ~ "Private",
    grepl("english", schooltype_1, ignore.case = TRUE) ~ "State",
    grepl("state", schooltype_1, ignore.case = TRUE) ~ "State",
    grepl("internation", schooltype_1, ignore.case = TRUE) ~ "International",
    TRUE ~ schooltype_1
    ))|>
  mutate(major_relabel = case_when(
    grepl("psych", major, ignore.case = TRUE) ~ "Psychology",
    grepl("degree", major, ignore.case = TRUE) ~ "Psychology",
    grepl("bs", major, ignore.case = TRUE) ~ "Psychology",
    TRUE ~ major  
  ))|>
  write_csv("derivative/cleaned_demo_UK.csv")
```

## Typing Speed Task

```{r}

typing_df <- combined_data |>
  dplyr::select(participant, group, typing_rt, typing_score, typing_response) |>
  mutate(participant = as.character(participant),
         group = as.character(group),
          typing_rt = as.numeric(typing_rt),  
         typing_score = as.integer(typing_score),
         typing_response = as.character(typing_response))|>
  filter(!is.na(typing_rt))|>
  mutate(error_typing = ifelse(typing_score != 1, 1, 0)) |>
  group_by(participant, group)|>
  summarise(n_typing = sum(typing_score == 1),
            median_typing = median(typing_rt[typing_score == 1]),
            mean_typing = mean(typing_rt[typing_score == 1]),
            acc_typing = n_typing/62*100,
            error_rate_typing = mean(error_typing))|>
  write_csv("derivative/typing_score_BU.csv")
```

## Multiplication Fluency Task (Typing)

```{r}

practice_prob = c("2 × 10 =", "1 × 7 =", "2 × 11 =")

mult_df <- combined_data |>
  dplyr::select(participant, group, fluency_rt, fluency_score, problem) |>
    mutate(participant = as.character(participant),
         group = as.character(group),
          fluency_rt = as.numeric(fluency_rt),  
         fluency_score = as.integer(fluency_score),
         problem = as.character(problem))|>
  filter(!is.na(problem))|>
  filter(!problem %in% practice_prob)|>
    group_by(participant, group)|>
  summarise(n_fluency = sum(fluency_score == 1),
            n_wrong = sum(fluency_score != 1),
            acc_fluency = n_fluency / 60 * 100,
            composite_fluency = ((n_fluency * 1) - (n_wrong * 0.5)) / 60 * 100,
            median_fluency = median(fluency_rt[fluency_score == 1]),
            mean_fluency = mean(fluency_rt[fluency_score == 1])) |> 
  write_csv("derivative/fluency_score_BU.csv")


# Calculate the mean fluency score
mult_df$n_fluency <- as.numeric(mult_df$n_fluency)
mean_fluency <- mean(mult_df$n_fluency)
min_fluency <- min(mult_df$n_fluency)
max_fluency <- max(mult_df$n_fluency)

print(mean_fluency)
print(min_fluency)
print(max_fluency)
```

## VPT

vpt score is the mean of last three correct blocks.

```{r}

vpt_df <- combined_data |>
  dplyr::select(participant, group, vpt_rt, vptCorrect, noOfBlocks, trialType) |>
    mutate(participant = as.character(participant),
         group = as.character(group),
          vpt_rt = as.numeric(vpt_rt),  
         vptCorrect = as.logical(vptCorrect),
         noOfBlocks = as.integer(noOfBlocks),
         trialType = as.character(trialType))|>
  filter(!is.na(trialType)) |>
  filter(!trialType == "practice trial") |>
  filter(vptCorrect == TRUE)|>
  group_by(participant, group)|>
  arrange(participant, desc(trialType)) |>
  slice(1:3) |>
  summarise(max_vpt = max(noOfBlocks),
            mean_vpt = mean(noOfBlocks))|>
  write_csv("derivative/vpt_score_BU.csv")
    

# Calculate the mean vpt score
vpt_df$max_vpt <- as.numeric(vpt_df$max_vpt)
vpt_df$mean_vpt <- as.numeric(vpt_df$mean_vpt)

mean_vpt <- mean(vpt_df$mean_vpt)
min_vpt <- min(vpt_df$mean_vpt)
max_vpt <- max(vpt_df$mean_vpt)

print(mean_vpt)
print(min_vpt)
print(max_vpt)
```

## Digit Span

There are two scores for Digit Span: Egner and WAIS

```{r}

#Egner Score

egner_df <- combined_data |>
  dplyr::select(participant, group, audio_rt, DS_score, digitSpan, digits_audioStim, typeDS) |>
   filter(typeDS == "EGNER") |>
    mutate(participant = as.character(participant),
         group = as.character(group),
          audio_rt = as.numeric(audio_rt),  
         DS_score = as.integer(DS_score),
         digitSpan = as.integer(digitSpan),
         digits_audioStim = as.character(digits_audioStim))|>
  filter(DS_score == 1) |>
  group_by(participant, group)|>
  arrange(participant, desc(digitSpan)) |>
  slice(1:3) |>
  summarise(max_egner = max(digitSpan),
            mean_egner = mean(digitSpan))|>
  write_csv("derivative/egner_score_BU.csv")

# WAIS score

wais_df <- combined_data |>
  dplyr::select(participant, group, audio_rt, DS_score, digitSpan, digits_audioStim, typeDS) |>
   filter(typeDS == "WAIS") |>
    mutate(participant = as.character(participant),
         group = as.character(group),
          audio_rt = as.numeric(audio_rt),  
         DS_score = as.integer(DS_score),
         digitSpan = as.integer(digitSpan),
         digits_audioStim = as.character(digits_audioStim))|>
  filter(DS_score == 1) |>
  group_by(participant, group)|>
  arrange(participant, desc(digitSpan)) |>
  slice(1:3) |>
  summarise(max_wais = max(digitSpan),
            mean_wais = mean(digitSpan))|>
  write_csv("derivative/wais_score_BU.csv")

merged_ds <- left_join(egner_df, wais_df, by = c("participant", "group")) |>
  write_csv("derivative/ds_summary_UK.csv")
```

## Stroop Comparison

```{r}


stroop_df <- combined_data |>
  dplyr::select(participant, group, stroopResp.rt, stroopResp.corr, 
                stroopCond, displayProblem, numDistance, Dims) |>
  filter(!is.na(displayProblem)) |>
   filter(stroopCond %in% c("physical", "magnitude")) |>
    mutate(participant = as.character(participant),
         group = as.character(group),
          stroopResp.rt = as.numeric(stroopResp.rt),  
         stroopResp.corr = as.integer(stroopResp.corr),
         numDistance = as.integer(numDistance),
         displayProblem = as.character(displayProblem),
         Dims = as.character(Dims))|>
  write_csv("derivative/stroop_trials_BU.csv")

## -----------------------------------------------

# physical Stooop - RT
phy_distance_df <- stroop_df |>
  filter(stroopCond == "physical") |>
  filter(stroopResp.corr == 1) |>
  mutate(trials_per_dist = if_else(numDistance == "0", 24, 16))|>
  group_by(participant, group, numDistance, trials_per_dist) |>
  summarise(n_trial = n(), 
            mean_rt = mean(stroopResp.rt))|>
  mutate(acc = (n_trial / trials_per_dist) * 100)|>
  dplyr::select(-c(trials_per_dist, n_trial))|>
    pivot_wider(names_from = numDistance,
              values_from = c(mean_rt, acc),
              names_prefix = "_P_")

# physical Stooop
phy_stroop_df <- stroop_df |>
  filter(stroopCond == "physical") |>
  filter(stroopResp.corr == 1)|>
  mutate(trials_per_dist = if_else(numDistance == "0", 24, 16))|>
  group_by(participant, group, Dims) |>
  summarise(n_trial = n(), 
            mean_rt = mean(stroopResp.rt),
            acc = n_trial/24*100)|>
  ungroup()|>
  dplyr::select(-n_trial)|>
  pivot_wider(names_from = Dims,
              values_from = c(mean_rt, acc),
              names_prefix = "_P_")

## -----------------------------------------------

# magnitude Stroop

mag_distance_df <- stroop_df |>
  filter(stroopCond == "magnitude") |>
  filter(stroopResp.corr == 1) |>
  group_by(participant, group, numDistance) |>
  summarise(n_trial = n(), 
            mean_rt = mean(stroopResp.rt),
            acc = n_trial/24*100)|>
  dplyr::select(-c(n_trial))|>
    pivot_wider(names_from = numDistance,
              values_from = c(mean_rt, acc),
              names_prefix = "_M_")

mag_stroop_df <- stroop_df |>
  filter(stroopCond == "magnitude") |>
  filter(stroopResp.corr == 1)|>
  mutate(trials_per_dist = if_else(numDistance == "0", 24, 16))|>
  group_by(participant, group, Dims) |>
  summarise(n_trial = n(), 
            mean_rt = mean(stroopResp.rt),
            acc = n_trial/24*100)|>
  ungroup()|>
  dplyr::select(-n_trial)|>
  pivot_wider(names_from = Dims,
              values_from = c(mean_rt, acc),
              names_prefix = "_M_")

## -----------------------------------------------------------------------

# UK
merged_stroop <- left_join(phy_distance_df, phy_stroop_df, by = c("participant", "group")) |>
  left_join(mag_distance_df, by = c("participant", "group")) |>
  left_join(mag_stroop_df, by = c("participant", "group"))|>
  write_csv("derivative/stroop_summary_UK.csv")


```

## Multiplication Verification Task

```{r}

veri_df <- combined_data |>
  dplyr::select(participant, group, veriStim_resp.rt, veriStim_resp.corr, mult_type,
         error_distance, interferenceScore, problemType, problemSize,
         interferenceLevel, mult_problem) |>
  filter(!is.na(mult_problem)) |>
  filter(mult_type != "practice") |>
  mutate(participant = as.character(participant),
         group = as.character(group),
         veriStim_resp.rt = as.numeric(veriStim_resp.rt),  
         veriStim_resp.corr = as.integer(veriStim_resp.corr),
         error_distance = as.integer(error_distance),
         interferenceScore = as.integer(interferenceScore),
         problemSize = as.character(problemSize),
         problemType = as.character(problemType),
         interferenceLevel = as.character(interferenceLevel),
         mult_type = as.character(mult_type))|>
  write_csv("derivative/veri_trials_BU.csv")

veri_performance <- veri_df |>
  filter(veriStim_resp.corr == 1) |>
  group_by(participant, group, mult_type) |>
  summarise(n_trial = n(), 
            mean_rt = mean(veriStim_resp.rt)) |>
  ungroup()|>
  pivot_wider(names_from = mult_type,
              values_from = c(n_trial, mean_rt),
              names_sep = "_")|>
  mutate(acc_veri = (n_trial_lure + n_trial_correct)/288 * 100)|>
  mutate(veri_performance = mean_rt_lure - mean_rt_correct)|>
  write_csv("derivative/veri_summary_UK.csv")
  
```
